---
title: "Using omicidx with BigQuery"
author: 
  - Vince Carey^[stvjc@channing.harvard.edu]
vignette: >
  %\VignetteIndexEntry{Using omicidx with BigQuery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output: 
  BiocStyle::html_document:
    number_sections: yes
    theme: united
    toc: yes
---

```{r init, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(BiocStyle)
library(magrittr)
library(bigrquery)
library(dplyr)
```

# Introduction

This vignette can be used if the following code can succeed.
```{r setup2, eval=FALSE}
bq_auth() # may need to do some gcloud configuration
con = bigrquery::dbConnect(bigquery(), 
    project="isb-cgc-01-0006", 
    dataset="omicidx", billing=Sys.getenv("BQ_BILLING"))
```


This vignette reviews basic aspects of interacting with omicidx as
exposed through Google BigQuery.

## Setup

See the basic [omicidx documentation](http://omicidx.cancerdatasci.org/docs/bigquery/setup/)
to establish an account for BigQuery.  The documentation also indicates how to
set up a project for billing.  Charges for a query depend on the quantity of data
scanned.

The following commands establish a connection to the omicidx dataset
in BigQuery.  This resource is updated approximately monthly.

```{r setup, eval=FALSE}
library(bigrquery)
library(dplyr)
bq_auth() # may need to do some gcloud configuration, supply gargle_oauth_email for identity
con = bigrquery::dbConnect(bigquery(), 
    project="isb-cgc-01-0006", 
    dataset="omicidx", billing=[provide billing code])
```
Once authentication has succeeded, the available tables
may be listed.  If you do not provide a billing code, certain
operations that don't involve scanning tables can succeed, but
select and filter operations will fail because they involve
creating temporary tables.

```{r lktabs, eval=FALSE}
dbListTables(con)
con %>% tbl("sra_study") %>% 
   select(study_type) %>% 
   group_by(study_type) %>% 
   summarise(n=n())
```


## Inspecting a table

